---
title: "satR - Global Mean Surface Air Temperature"
output:
  html_document:
    toc: true
    theme: united   
  pdf_document:
    toc: true
    pandoc_args: --listings 
    includes:
      in_header: preamble.tex
---

```{r global_options, include=FALSE}
library(knitr)
library(tidyr)
library(tidyverse)
library(ncdf4) # for NetCDF
library(colorspace)
library(cowplot)
library(ggforce)
library(quantmod)
library(ggplot2)
library(ggridges) # for geom_density_ridges
library(viridis)  # Load viridis for the viridis palette
opts_chunk$set(fig.align="center", fig.height=4, fig.width=5.5)

```

## SST 

```{r }

test_csv_data <- 
  read.csv("./sat_data/HadCRUT.5.0.2.0.analysis.summary_series.global.annual.csv")

head(test_csv_data)
print(colnames(test_csv_data)[2])

plot(test_csv_data$Time, test_csv_data$Anomaly..deg.C.)

test_csv_plot <- 
    test_csv_data %>%
        ggplot(
            aes(
                y = Anomaly..deg.C.,
                x = Time
            )
        ) + 
        geom_errorbar(
                      aes(
                          ymin = Lower.confidence.limit..2.5.., 
                          ymax = Upper.confidence.limit..97.5..,
                          color = 'red'),
                      size = 1.25
        ) +
        geom_point(size = 3.5) +
        scale_color_identity() +
        scale_x_continuous(name = bquote('Time'), 
#                           limits = c(1100,1700),
#                           breaks = c(1100, 1200, 1300, 1400, 1500, 1600, 1700),
#                           labels = c("1100", "1200", "1300", "1400", "1500", "1600", "1700"),#,
                           expand = expansion(mult = c(0.05,0.05))
        ) + 
        scale_y_continuous(name = "Surface Air Temperature Anomaly", 
#                           limits = c(0,28000), 
#                           breaks = c(0, 7000, 14000, 21000, 28000),
#                           labels = c("0", "7000", "14000", "21000", "28000"),#,
                           expand = expansion(mult = c(0.1,0.1))
        ) +
        ggtitle(
#            bquote('Raman Spectra of Samples from \n Haynesville Formation')
            bquote("Time Evolution of Global Surface Air Temperature Anomaly (°C)")
        ) + 
        theme_bw() +
        theme(
            plot.title = element_text(hjust = 0.5, size = 30),
            axis.title = element_text(size = 24),
            axis.text = element_text(size = 18),
            panel.grid.major.x = element_line(size=0.6),
#            panel.grid.major.x = element_blank(),
#            panel.grid.minor.x = element_blank(),
#            panel.grid.major.x = element_line( size=.1, color="black" ),
#            panel.grid.major.y = element_line(size=0.6),
#            panel.grid.major.y = element_blank(),
#            panel.grid.minor.y = element_blank()
            panel.border = element_rect(size = 1)
        )

test_csv_plot

aspect_ratio <- 1.4

ggsave("test_csv_plot.png", 
       test_csv_plot, 
       height = 10 , 
       width = 10 * aspect_ratio, 
       path = "./"
)

test_nc_data <- 
  nc_open("./sat_data/HadCRUT.5.0.2.0.analysis.summary_series.global.annual.nc")

print(test_nc_data)

print(attributes(test_nc_data$var))
print(attributes(test_nc_data$dim))

#test_sst <-
#  ncvar_get(test_nc_data, "sst")
#  
#print(dim(test_sst))
#
#test_sst <-
#  ncvar_get(test_nc_data, "sst")
#  
#head(test_sst)


